\documentclass[10pt]{article}
\input{common_preamble.tex}
\hypersetup{
  pdftitle={Ian Johnson},
  pdfkeywords={resume},
  pdfauthor={Ian Johnson},
  pdfsubject={Ian Johnson's resume}
}
\begin{document}
\begin{center}
  {\Large\bfseries Ian Johnson} \\
  2925 Rensselaer Court, Vienna, VA 22181 \\
  (703) 819--8495 \\
  \href{mailto:IanTimothyJohnson@gmail.com}{IanTimothyJohnson@gmail.com}
\end{center}

\section*{Summary}
I am a quick and versatile learner, adaptable to a variety of challenging
situations and tasks.  I have a strong background in mathematics, as well as
experience in computer programming.

\section*{Education}
\entry{University of Virginia}
{May 2017}
{B.A. in Mathematics (advanced track) and Physics}
{Overall G.P.A.: 3.96}
\begin{itemize}
\item Echols Scholar
\item Edwin E. Floyd Prize in Mathematics (2017)
\item Intermediate Honors (2016)
\end{itemize}

\section*{Experience}
\entry{Volunteer Tutor}
{September 2017--Present}
{FACETS}
{Centreville, VA}
\begin{itemize}
\item Teach computer, math and English skills to adults and children
  in a low-income community.
\item Provide proactive technical support to community center.
\end{itemize}

\entry{Undergraduate Physics Researcher}
{April 2015--September 2017}
{UVa Solid Polarized Target Group}
{Charlottesville, VA}
\begin{itemize}
\item Develop simulations and mathematical models from systems of
  differential equations and real data.
\item Design and implement software to assist in lab tasks.
\end{itemize}

\entry{Undergraduate Mathematics Researcher}
{May 2016--July 2017}
{University of Virginia}
{Charlottesville, VA}
\begin{itemize}
\item Apply individual study of new material to research efforts.
\item Collaborate with research adviser to investigate novel concepts.
\end{itemize}

\entry{Vice President and Secretary}
{May 2015--May 2017}
{Kinetic Sound}
{Charlottesville, VA}
\begin{itemize}
\item Co-founded successful student organization.
\item Coordinate logistics of large-scale events with over one hundred
  attendees.
\end{itemize}

\section*{Skills}
\textbf{Computer Proficiency}
\begin{itemize}
\item Experienced with Windows and GNU/Linux systems (day-to-day usage
  and basic administration)
\item Proficient in Microsoft Office (Word, Powerpoint, Excel) and
  equivalent products
\end{itemize}

\textbf{Programming}
\begin{itemize}
\item Languages: C, JavaScript, Rust, LabVIEW, C++
\item Web tools: HTML, CSS, JSON
\item Development tools: Git, make, NPM/Yarn, GCC, POSIX shell
  scripting
\item GitHub: \url{https://github.com/ianprime0509}
\end{itemize}

\section*{Publications and presentations}
\begin{itemize}
\item Chain Posets (\url{https://arxiv.org/abs/1802.05813})
\item Automated Microwave Frequency Control in Dynamic Nuclear
  Polarization Experiments
  (\url{http://meetings.aps.org/link/BAPS.2016.APR.K10.2})
\end{itemize}

\end{document}
